\TheTitle

### 2019-02-20 Paper1/introduction.tex
added file structure

\documentclass[3p]{elsarticle}

% Packages and macros go here
\usepackage{bm}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{color}
\usepackage{bm}
\usepackage{graphicx}
%\usepackage{subfig}
\usepackage{subcaption}
%\usepackage[]{algorithm2e}
%\usepackage{algorithmic}
%\usepackage{algorithmicx}
\usepackage[linesnumbered,ruled]{algorithm2e}

\usepackage{lipsum}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithmic}
\ifpdf
  \DeclareGraphicsExtensions{.eps,.pdf,.png,.jpg}
\else
  \DeclareGraphicsExtensions{.eps}
\fi

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

\DeclareMathOperator*{\argmin}{arg\,min}

\makeatletter
\newsavebox\myboxA
\newsavebox\myboxB
\newlength\mylenA

\newcommand*\xoverline[2][0.75]{%
    \sbox{\myboxA}{$\m@th#2$}%
    \setbox\myboxB\null% Phantom box
    \ht\myboxB=\ht\myboxA%
    \dp\myboxB=\dp\myboxA%
    \wd\myboxB=#1\wd\myboxA% Scale phantom
    \sbox\myboxB{$\m@th\overline{\copy\myboxB}$}%  Overlined phantom
    \setlength\mylenA{\the\wd\myboxA}%   calc width diff
    \addtolength\mylenA{-\the\wd\myboxB}%
    \ifdim\wd\myboxB<\wd\myboxA%
       \rlap{\hskip 0.5\mylenA\usebox\myboxB}{\usebox\myboxA}%
    \else
        \hskip -0.5\mylenA\rlap{\usebox\myboxA}{\hskip 0.5\mylenA\usebox\myboxB}%
    \fi}
\makeatother

\journal{arXiv.org}

%strongly recommended
%\numberwithin{theorem}{section}

% Declare title and authors, without \thanks
\newcommand{\TheTitle}{A semi-intrusive Code Framework for Uncertainty Quantification}

\date{\today}

% Sets running headers as well as PDF title and authors
%\headers{\RunningTitle}{\TheAuthors}

\usepackage{amsopn}
\DeclareMathOperator{\diag}{diag}
%\DeclareMathOperator{\argmin}{arg\min}

% FundRef data to be entered by SIAM
%<funding-group>
%<award-group>
%<funding-source>
%<named-content content-type="funder-name"> 
%</named-content> 
%<named-content content-type="funder-identifier"> 
%</named-content>
%</funding-source>
%<award-id> </award-id>
%</award-group>
%</funding-group>

\def\lambdabar{\xoverline{\bm{\lambda}}}
\def\lambdabarjn{\lambdabar_j^n}

\newcommand{\commentRyan}[1]{{\Large{\textcolor{red}{\newline[RYAN: #1]\newline}}}}
\newcommand{\commentJonas}[1]{{\Large{\textcolor{blue}{\newline[JONAS: #1]\newline}}}}

\begin{document}

\begin{frontmatter}

\title{\TheTitle}

\author[adressJonas]{Jonas Kusch}
\author[adressJannick]{Jannick Wolters}

\address[adressJonas]{Karlsruhe Institute of Technology, Karlsruhe,
    jonas.kusch@kit.edu}
\address[adressJannick]{Karlsruhe Institute of Technology, Karlsruhe, jannick.wolters@kit.edu}

\begin{abstract}
Methods for quantifying the effects of uncertainties in hyperbolic problems can be divided into intrusive and non-intrusive techniques. Intrusive methods require the implementation of a new code and yield

\end{abstract}

\begin{keyword}
conservation laws, hyperbolic, intrusive, UQ, IPM, SG, Collocation
\end{keyword}

\end{frontmatter}
\section{Introduction}
Hyperbolic equations play an important role in various research areas such as fluid dynamics or plasma physics. Efficient numerical methods combined with robust implementations are available for these problems, however they do not account for uncertainties which can arise in measurement data or modeling assumptions. Including the effects of uncertainties in differential equations has become an important topic in the last decades. %Examples include computational fluid dynamics \cite{bijl2013uncertainty}.

@@

\section{Methods of Uncertainty Quantification}
\subsection{Collocation}
\subsection{Stochastic Galerkin}
\subsection{Intrusive Polynomial Moment Method}
\section{Method discussion}
\begin{itemize}
	\item kleinere Fehler [11]
	\item Programmieraufwand [31]
	\item zweiabhängig
	\item adaptiv (breack up black box approach )
	\item grobe Auflösung für Momente 
\end{itemize}
\section{UQCreator}
\subsection{Adaptivity}
\subsection{restart IPM} %relay(-strategy) IPM?
\subsection{one-shot IPM}
\subsection{adaptive IPM}
\section{Results}
\subsection{2D Euler flow over NACA0012}
\begin{itemize}
	\item AoA study
	\item AoA + Ma number + mehr ?
\end{itemize}
\subsection{2D shallow water dam break}

\bibliographystyle{unsrt}  
\bibliography{references}
\end{document}

>>>>

\section{Introduction}
Hyperbolic equations play an important role in various research areas such as fluid dynamics or plasma physics. Efficient numerical methods combined with robust implementations are available for these problems, however they do not account for uncertainties which can arise in measurement data or modeling assumptions. Including the effects of uncertainties in differential equations has become an important topic in the last decades. %Examples include computational fluid dynamics \cite{bijl2013uncertainty}.

@@
